A survey of HTTP caching options on the open Web

### 2015-01-13 sanity/paper1.tex
Heuristic plots
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@978 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{figure}[ht!]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardall.pdf}}
  \caption{Barplot of all standard-compliant freshness lifetimes
    found. The first bin are the cases where caching is explicitly
    prohibited. The next bins are for lifetimes, where the values are
    grouped if they are on the order of seconds, minutes, hours, etc,
    i.e. the second bin counts the lifetimes in the interval [1,59]
    seconds, etc.}
  \label{fig:hardall}
\end{figure}

@@

\begin{figure}[ht!]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardtable.pdf}}
  \caption{Mosaic Plot. Divided by type of resource on the vertical
    axis and by the same bins as in Figure~\ref{fig:hardall} on the
    horizontal axis. }
  \label{fig:hardtable}
\end{figure}

@@

We were able to compute a heuristic lifetime for 554 resources, a
larger number than standards-compliant resources. In Figure\todo{add all
  heuristics figure}, we see that the distribution of lifetimes are
radically different from the case in Figure\todo{ref fig:allhard}. In
this case, we may cache many resources for months. Only a handful of
resources had changed in the last minutes. Since this is based
on actual times since last modifications, this suggests that many
resources should have had explicit cache headers with very long
lifetimes. This is supported by DyLDO\cite{dyldo2}, which concludes that:
\begin{quote}
[...] We found that 62.2\% of documents didn’t change over the six
months and found that 51.9\% of domains were considered static.
\end{quote}
This agrees well with that 60\% of the simple heuristic lifetimes are
in the month range.

Moreover, by inspecting Figure\todo{add heuristic table figure}, we
note that the difference between different types of resources is much
smaller. This is confirmed by a $\chi^2$ test that yields \pvalue =
0.02.

>>>>

\begin{figure}[ht]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardall.pdf}}
  \caption{Barplot of all standard-compliant freshness lifetimes
    found. The first bin are the cases where caching is explicitly
    prohibited. The next bins are for lifetimes, where the values are
    grouped if they are on the order of seconds, minutes, hours, etc,
    i.e. the second bin counts the lifetimes in the interval [1,59]
    seconds, etc.}
  \label{fig:hardall}
\end{figure}

@@

\begin{figure}[ht]
  \centerline{%
    \includegraphics[width=.9\textwidth]{hardtable.pdf}}
  \caption{Mosaic Plot. Divided by type of resource on the vertical
    axis and by the same bins as in Figure~\ref{fig:hardall} on the
    horizontal axis. }
  \label{fig:hardtable}
\end{figure}

@@

\begin{figure}[th!]
  \centerline{%
    \includegraphics[width=.9\textwidth]{heuristicall.pdf}}
  \caption{Barplot of all simple heuristic freshness lifetimes
    found. Bins as in Figure~\ref{fig:hardall}.}
  \label{fig:heuristicall}
\end{figure}

We were able to compute a heuristic lifetime for 554 resources, a
larger number than standards-compliant resources. In
Figure~\ref{fig:heuristicall}, we see that the distribution of
lifetimes are radically different from the case in
Figure~\ref{fig:hardall}. In this case, we may cache many resources
for months. Only a handful of resources had changed in the last
minutes. Since this is based on actual times since last modifications,
this suggests that many resources should have had explicit cache
headers with very long lifetimes. This is supported by
DyLDO\cite{dyldo2}, which concludes that:
\begin{quote}
[...] We found that 62.2\% of documents didn’t change over the six
months and found that 51.9\% of domains were considered static.
\end{quote}
This agrees well with that 60\% of the simple heuristic lifetimes are
in the month range.

Moreover, by inspecting Figure~\ref{fig:heuristictable}, we
note that the difference between different types of resources is much
smaller. This is confirmed by a $\chi^2$ test that yields \pvalue =
0.02.

\begin{figure}[hb!]
  \centerline{%
    \includegraphics[width=.9\textwidth]{heuristictable.pdf}}
  \caption{Mosaic Plot. Divided by type of resource on the vertical
    axis and by the same bins as in Figure~\ref{fig:hardall} on the
    horizontal axis. }
  \label{fig:heuristictable}
\end{figure}
